Comparison and Evaluation of Popular Syntax Highlighting Themes in Terms of Color Correlated Temperature values

### 2022-04-22 doc/manuscript.tex
.

\title{A novel approach to the theme for syntax highlighting selection based on Color Correlated Temperature in terms of blue light hazard}

@@

\begin{figure}[h]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tabledual}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      y=12mm,
    ]
      \addplot table[x=dark,y=index] {\tabledual};
      \addplot table[x=light,y=index] {\tabledual};
      \legend {Dark, Light};
      \draw[thick,dashed] (axis cs: 6500,0) -- (axis cs: 6500,8.5) node[anchor=east]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{Dark-Light CCT value comparison of themes in pairs}
  \label{fig:dark-light-pair-compare}
\end{figure}

@@

\begin{figure}[h]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tabledark}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      xmin=5000,
      y=12mm,
    ]
      \addplot table[x=ccts,y=index] {\tabledark};
      \draw[thick,dashed] (axis cs: 6500,0) -- (axis cs: 6500,8.5) node[anchor=east, yshift=-7.5mm]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{CCT value comparison of dark themes}
  \label{fig:dark-compare}
\end{figure}

>>>>

%\title{A novel approach to the theme for syntax highlighting selection based on Color Correlated Temperature in terms of blue light hazard}

\title{Comparison and Evaluation of Popular Syntax Highlighting Themes in Terms of Color Correlated Temperature values}

@@

\begin{figure}[h]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tabledual}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      y=11mm,
    ]
      \addplot table[x=dark,y=index] {\tabledual};
      \addplot table[x=light,y=index] {\tabledual};
      \legend {Dark, Light};
      \draw[thin,dashed] (axis cs: 6500,0) -- (axis cs: 6500,8.5) node[anchor=west, yshift=-14mm]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{Dark-Light CCT value comparison of themes in pairs}
  \label{fig:dark-light-pair-compare}
\end{figure}

@@

\begin{figure}[H]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tabledark}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      xmin=5000,
      y=8mm,
    ]
      \addplot table[x=ccts,y=index] {\tabledark};
      \draw[thin,dashed] (axis cs: 6500,0) -- (axis cs: 6500,8.5) node[anchor=east, yshift=-8.0mm]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{CCT value comparison of dark themes}
  \label{fig:dark-compare}
\end{figure}

\pgfplotstableread[col sep=comma,text indicator="]{./data/themes-light.csv}\lighttable
\pgfplotstabletranspose[colnames from=themes]\tablelight{\lighttable}

\begin{figure}[H]
  \begin{tikzpicture}
    \begin{axis}[
      xbar,
      tick label style={font=\footnotesize},
      ytick=data,
      yticklabels from table={\tablelight}{colnames},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
      },
      scaled x ticks=false,
      xlabel=$CCT (K)$,
      xmin=5000,
      y=8mm,
    ]
      \addplot [fill=red!30!white] table[x=ccts,y=index] {\tablelight};
      \draw[thin,dashed] (axis cs: 6500,0) -- (axis cs: 6500,8.5) node[anchor=east, yshift=-8.0mm]{D65};
    \end{axis}
  \end{tikzpicture}
  \caption{CCT value comparison of light themes}
  \label{fig:light-compare}
\end{figure}
